\documentclass[conference]{IEEEtran}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{url}
\usepackage{hyperref}
\usepackage{array}
\usepackage{float}
\usepackage{subcaption}
\usepackage{tikz}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usetikzlibrary{shapes.geometric, arrows.meta, positioning, calc, patterns, fit}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\begin{document}

\title{SecureBank: A Hybrid Statistical and Neural Network Framework for Continuous Behavioral Authentication on Mobile Banking Platforms}

\author{
\IEEEauthorblockN{Tejus Kapoor}
\IEEEauthorblockA{\textit{Dept. of Computer Science and Engg.} \\
\textit{Graphic Era (Deemed to be University)}\\
Dehradun, India \\
tejus180104@gmail.com}
\and
\IEEEauthorblockN{Tanush Malhotra}
\IEEEauthorblockA{\textit{Dept. of Computer Science and Engg.} \\
\textit{Graphic Era (Deemed to be University)}\\
Dehradun, India \\
tanushmalhotra0018@gmail.com}
\and
\IEEEauthorblockN{Bela Diwan}
\IEEEauthorblockA{\textit{Dept. of Computer Science and Engg.} \\
\textit{Graphic Era (Deemed to be University)}\\
Dehradun, India \\
beladiwan001@gmail.com}
\and
\IEEEauthorblockN{Gautam Nautiyal}
\IEEEauthorblockA{\textit{Dept. of Computer Science and Engg.} \\
\textit{Graphic Era (Deemed to be University)}\\
Dehradun, India \\
gautamnautiyal943@gmail.com}
}

\maketitle

% ─── ABSTRACT ──────────────────────────────────────────────
\begin{abstract}
Banking apps on Android authenticate you once. After that --- nothing. The session stays open, and whoever picks up the phone is trusted implicitly until logout or timeout. \textit{SecureBank} is our attempt at fixing this gap. It is a working Android prototype that monitors three behavioral channels throughout a session: PIN-entry keystroke timing captured through a custom numeric pad, touch interaction patterns (taps, swipes, scrolls) intercepted via Compose's pointer input system, and device orientation derived from the accelerometer and gyroscope. Two parallel detection tracks run on the handset itself, with no server component. The first track compares rolling session averages against the login baseline using Z-scores. The second constructs a 124-dimensional deviation feature vector and pushes it through a small MLP --- weights stored as a JSON file, inference implemented as plain Kotlin matrix multiplication, no TensorFlow or ONNX dependency at all. Data came from 8 participants on physical devices. Because that pool was too small to train reliably, we expanded it to 58 participants through a calibrated synthetic generator built on Dirichlet profile blending, age-adjusted motor noise drawn from published ergonomics literature, and Ornstein--Uhlenbeck processes for realistic accelerometer traces. On the resulting 379-session corpus, Random Forest achieved 89.71\% accuracy (AUC\,=\,0.979, EER\,=\,8.71\%), while the on-device MLP reached 87.60\% (AUC\,=\,0.938). The feature importance analysis produced a result we did not anticipate: accelerometer tilt and tap-to-swipe ratio dominated the rankings, pushing keystroke dynamics well below expectations. A fused risk score maps onto four graduated response levels from passive monitoring through forced logout.
\end{abstract}

\begin{IEEEkeywords}
behavioral biometrics, continuous authentication, keystroke dynamics, mobile security, neural network, anomaly detection, touch dynamics, inertial sensors, Android
\end{IEEEkeywords}

% ====================================================================
\section{Introduction}
% ====================================================================

Consider what happens after a user types their PIN into PhonePe, checks a balance, then sets the phone on the table to stir their coffee. Thirty seconds pass. The session is live. The authentication gate was crossed five minutes ago and the app no longer distinguishes between the account holder and a stranger. Anybody who picks up the device inherits full access.

This is not hypothetical. The ECB's card fraud report~\cite{ecb2022} documented a 23\% year-on-year rise in unauthorized mobile transactions. The FBI's IC3 flagged the same trend in its 2023 report~\cite{fbi2023}. Yet the dominant authentication model across mobile banking remains gate-and-forget: verify once at login, then trust blindly until session expiry.

Behavioral biometrics offers a different approach. Decades of research have shown that keystroke rhythm, swipe patterns, and phone-holding posture are measurably person-specific~\cite{teh2017keystroke,frank2013touchalytics,bo2013silentsense}. Lab results are strong --- equal error rates below 5\% in controlled settings are common. But translating lab demonstrations into production-ready systems has proven stubborn. The published literature overwhelmingly addresses algorithmic novelty~\cite{zheng2020survey}; questions about battery impact, inference latency, sensor API limitations on real handsets, and integration with actual application logic receive far less attention.

SecureBank was built to close that gap. It is a working Android banking application --- login screen, account dashboard, fund transfer flow --- that silently records keystroke timing, touch interactions, and accelerometer/gyroscope readings from the moment a session begins. A hybrid detection engine running entirely on the handset blends statistical Z-score comparisons with neural-network inference. Rather than issuing a binary pass/fail, the system escalates its response gradually: at low risk nothing visible happens; at critical risk the user is forcibly logged out.

The contributions are as follows:

\begin{enumerate}
\item A fully functional Android prototype (Kotlin, Jetpack Compose, Hilt, Room) demonstrating continuous behavioral authentication within a realistic banking UI, not a standalone sensor-logging application.
\item A dual-track detection architecture combining Z-score deviation analysis with on-device MLP classification, fused through weighted score combination.
\item A feature engineering pipeline that transforms 42 raw session measurements into 124 enrollment-relative deviation features capturing both absolute and proportional drift from the user's baseline.
\item Pure-Kotlin neural network inference loading weights from a single JSON file, requiring no TensorFlow Lite, ONNX Runtime, or native library dependencies.
\item Evaluation across 379 sessions from 58 participants (8 real, 50 synthetic) under five-fold stratified cross-validation, comparing Random Forest, MLP, and One-Class SVM.
\end{enumerate}

Section~\ref{sec:related} surveys prior work. Section~\ref{sec:architecture} describes the application architecture and sensor collection subsystem. Feature engineering is covered in Section~\ref{sec:features}; the machine learning pipeline and training protocol in Section~\ref{sec:ml}. Results appear in Section~\ref{sec:results}, followed by a discussion of limitations and adversarial considerations in Section~\ref{sec:discussion}. Section~\ref{sec:conclusion} concludes.


% ====================================================================
\section{Related Work}
\label{sec:related}
% ====================================================================

\subsection{Keystroke Dynamics}

Typing-based identification has a longer history than most people realize. Monrose and Rubin~\cite{monrose1997keystroke} demonstrated in 1997 that inter-key latencies from password entry were sufficient to distinguish users at error rates below 10\%. Killourhy and Maxion~\cite{killourhy2009comparing} later produced what remains one of the most methodical benchmarks in the area: 51 subjects, 14 detection algorithms, the same fixed string typed repeatedly across sessions. Their best detectors achieved EERs between roughly 5\% and 12\%, depending on the algorithm family.

Porting this to mobile introduces a serious practical obstacle. Android's soft keyboard does not expose discrete key-down or key-up events to the hosting application --- only the resulting text reaches the app layer. Giuffrida et al.~\cite{giuffrida2014itsme} addressed this by implementing a custom input method editor that intercepts low-level touch coordinates underneath the keyboard surface. Buschek et al.~\cite{buschek2015touchalytics} took a less invasive route, supplementing estimated dwell times with spatial touch features such as contact area and finger position on the key. Our approach falls between these two strategies. General text input uses a fixed 80\,ms dwell estimate (the rationale and its consequences are discussed in Section~\ref{sec:discussion}), while PIN entry relies on a purpose-built numeric pad that captures genuine touch-down and touch-up timestamps along with per-key spatial data.

\subsection{Touch Patterns}

Frank et al.'s Touchalytics work~\cite{frank2013touchalytics} informed several of our early design choices. Their 30-feature stroke-trajectory representation achieved EERs of 2--3\%, though an important caveat applies: those numbers held within individual sessions and degraded noticeably in cross-session evaluation. This intra-versus-inter-session gap appears across much of the touch biometrics literature.

Bo et al.~\cite{bo2013silentsense} extended the feature space to include pressure and contact area, which improved robustness to session effects. A particular insight from their work shaped our own feature design: taps and swipes encode qualitatively distinct behavioral signals and should be treated separately. Our tap-to-total-event ratio turned out to rank among the strongest individual features --- a finding discussed in detail in Section~\ref{sec:results}.

\subsection{Motion and Sensor Data}

Smartphone accelerometers and gyroscopes capture aspects of motor behavior that the touchscreen cannot. Conti et al.~\cite{conti2011mobileauth} achieved below 7\% EER using accelerometer-derived gait features alone. Sitov\'{a} et al.~\cite{sitova2016hmog} proposed HMOG (Hand Movement, Orientation, and Grasp), a feature set fusing both inertial measurement unit sensors to characterize device-holding posture, reporting EERs in the 7--10\% range.

These results gave us confidence that motion-sensor data would contribute meaningful discriminative power. What we did not foresee was the extent of that contribution: motion features ended up occupying seven of the top ten positions in our importance rankings, decisively outweighing both keystroke and touch modalities.

\subsection{Multi-Modal and Continuous Systems}

Two design principles from the Patel et al.\ survey~\cite{patel2016continuous} directly influenced our architecture: sensor fusion across modalities and transparency to the end user. Khan and Hengartner~\cite{khan2014gait} provided supporting empirical evidence --- combining touch with gait data consistently outperformed either modality in isolation.

On the deep-learning side, Abuhamad et al.~\cite{li2020continuous} demonstrated that LSTMs applied to raw sensor streams can achieve strong accuracy, but at computational and memory costs that would be difficult to justify in a banking app running Compose UI, Room database transactions, and network operations concurrently on a mid-range chipset. We opted instead for aggregated statistical features fed into a compact feedforward network, accepting some ceiling on representational power in exchange for lightweight on-device execution.


% ====================================================================
\section{System Architecture}
\label{sec:architecture}
% ====================================================================

SecureBank follows the MVVM pattern standard in modern Android development, with an additional sensor collection layer operating beneath the view model tier. Fig.~\ref{fig:architecture} illustrates the layered structure.

\begin{figure}[htbp]
\centering
\resizebox{\columnwidth}{!}{%
\begin{tikzpicture}[
    layer/.style={draw, rounded corners, minimum width=7.2cm, minimum height=0.7cm, align=center, font=\footnotesize},
    arrow/.style={-{Stealth[length=2mm]}, thick},
    node distance=0.45cm
]
\node[layer, fill=blue!12] (ui) {\textbf{UI Layer} --- Jetpack Compose + Material 3};
\node[layer, fill=green!12, below=of ui] (vm) {\textbf{ViewModel Layer} --- AuthVM, BankingVM, ExperimentVM};
\node[layer, fill=orange!15, below=of vm] (domain) {\textbf{Domain Layer} --- BehaviorAnalyzer, MLInference, FeatureExtractor};
\node[layer, fill=yellow!15, below=of domain] (data) {\textbf{Data Layer} --- Room SQLite + Repositories};
\node[layer, fill=red!10, below=of data] (sensor) {\textbf{Sensor Layer} --- Keystroke $\vert$ Touch $\vert$ Accelerometer $\vert$ Gyroscope};

\draw[arrow] (sensor) -- node[right, font=\scriptsize] {events} (data);
\draw[arrow] (data) -- node[right, font=\scriptsize] {data flows} (domain);
\draw[arrow] (domain) -- node[right, font=\scriptsize] {risk scores} (vm);
\draw[arrow] (vm) -- node[right, font=\scriptsize] {UI state} (ui);

\node[draw, dashed, rounded corners, fill=gray!8, font=\scriptsize, text width=1.8cm, align=center, right=0.3cm of domain] (ml) {MLP Model\\(JSON weights)};
\draw[-{Stealth[length=1.5mm]}, dashed] (ml) -- (domain);

\end{tikzpicture}%
}
\caption{Layered architecture of SecureBank. Behavioral data flows upward from hardware sensors through persistence, feature extraction, and risk assessment to user-facing security actions.}
\label{fig:architecture}
\end{figure}

The entire codebase is Kotlin. UI is built with Jetpack Compose and Material 3; dependency injection uses Hilt; local persistence runs on Room backed by SQLite; concurrency relies on Kotlin Coroutines and Flows throughout. Minimum SDK level is 26; target is 34. We tested on three handsets --- a Redmi Note 11 (Snapdragon 680), a Samsung Galaxy A52, and a Pixel 6a --- chosen because they are representative of the mid-range hardware that dominates the Indian market where a system such as this would eventually be deployed.

\subsection{Behavioral Data Collection}

Three Hilt-injected singleton collector classes handle raw data capture. All three activate at session start and remain active until the session terminates.

\subsubsection{Keystroke Collector}
Building this component was the most frustrating part of the project. Android's stock keyboard --- whether Gboard, Samsung Keyboard, or an OEM variant --- does not surface individual key-down and key-up events to the host application. The app receives only the resulting text. Consequently, for general text fields, each character insertion is timestamped and assigned a fixed 80\,ms dwell time derived from average tap durations measured across our three test devices during the pilot phase. Flight time (the interval between consecutive \texttt{TextFieldValue} changes) is at least a genuine measurement, although the keyboard's autocorrect and prediction engine introduces variable latency between the physical tap and the character actually arriving in the field.

PIN entry is handled differently. We implemented a custom six-button numeric pad in Compose that intercepts \texttt{MotionEvent.ACTION\_DOWN} and \texttt{ACTION\_UP} directly, bypassing the system input method entirely. This yields actual dwell times, actual flight times, per-digit $(x, y)$ coordinates, and contact area measurements. The difference in data quality between this custom component and the standard keyboard is substantial, and it shows clearly in the feature importance analysis presented in Section~\ref{sec:results}.

At login, the keystroke collector stores captured data as the enrollment baseline. All subsequent analysis is measured against this reference.

\subsubsection{Touch Data Collector}
Every pointer event is intercepted through Compose's \texttt{pointerInput} modifier. Events are classified using straightforward geometric thresholds: displacement below 30\,dp with duration below 300\,ms registers as a TAP; displacement above 50\,dp registers as a SWIPE; long-press and scroll events have their own criteria. For each classified event, the collector logs start and end coordinates, duration, velocity ($v = \Delta d / \Delta t$), acceleration, contact area, and pressure. One device-specific issue worth noting: the Pixel 6a consistently reports zero for pressure on every touch event, which forced us to zero out that feature entirely for sessions collected on that handset.

Collected events are emitted as a Kotlin Flow and persisted through the repository layer.

\subsubsection{Sensor Data Collector}
Both the accelerometer and gyroscope register at \texttt{SENSOR\_DELAY\_UI}, yielding samples approximately every 60\,ms. Raw readings pass through a 10-sample moving-average filter before further processing. This filtering step proved essential: on the Redmi Note 11, unfiltered gyroscope output exhibited high-frequency oscillation that obscured the actual rotation signal. The Samsung A52 was somewhat better, but still benefited from smoothing.

Filtered accelerometer values are used to compute pitch and roll angles:

\begin{equation}
\theta = \arctan\!\left(\frac{a_y}{\sqrt{a_x^2 + a_z^2}}\right), \quad
\phi = \arctan\!\left(\frac{-a_x}{a_z}\right)
\end{equation}

A rule-based state classifier labels the device posture from these derived quantities. A flat orientation with minimal gyroscope activity maps to ON\_TABLE. Moderate tilt with low angular velocity maps to HELD\_IN\_HAND. Periodic acceleration spikes coupled with gyroscope activity map to WALKING. All other states default to STATIONARY. The classifier is deliberately simple, but the resulting state labels proved useful as contextual features for the downstream risk engine.

\subsection{Storage and Persistence}

All collected data is written to a local Room database. The \texttt{BehavioralRepository} class wraps the underlying DAOs and exposes aggregated session-level metrics --- mean dwell time, mean touch pressure, mean device tilt --- keyed by session identifier. A CSV export function was added separately to support the research workflow: pulling data off the device for processing in the Python-based ML training pipeline.


% ====================================================================
\section{Feature Engineering}
\label{sec:features}
% ====================================================================

Early iterations of our pipeline fed raw session-level statistics directly into the classifiers --- quantities such as ``mean dwell time = 58\,ms'' or ``average accelerometer Y = 3.2\,m/s$^2$.'' Classification accuracy was poor. Inspection of learned decision boundaries revealed that the models were separating users by their inherent baseline differences rather than distinguishing between genuine and impostor sessions for a given user. Two slow typists were being mapped to the same region of feature space regardless of whether they were the same person.

The breakthrough came from reframing the problem around enrollment-relative deviations. Instead of asking what a session's features look like in absolute terms, we ask how far each feature has moved from the value recorded during that user's enrollment. This single design change produced an approximately 12-percentage-point accuracy improvement on our held-out validation split.

\subsection{Raw Features}

Each session produces 42 scalar measurements, organized into three groups:

\textbf{PIN Keystroke (24 features):} Summary statistics of dwell and flight time distributions --- mean, standard deviation, median, 25th percentile, 75th percentile, and interquartile range --- plus skewness and kurtosis of dwell times. Spatial features include mean and standard deviation of touch coordinates ($x$, $y$) and contact area. Six per-digit-position rhythm values complete this group, each capturing the characteristic timing of pressing a specific digit in the PIN sequence. During pilot testing we observed that digit-position timing was remarkably consistent within individuals: the thumb reaching for position three on the bottom row produces a measurably different latency profile than the index finger stretching toward position one at the top.

\textbf{Touch (9 features):} Mean and standard deviation of event duration; mean, standard deviation, and maximum of swipe velocity; mean and standard deviation of acceleration; the ratio of tap events to total touch events; and total event count.

\textbf{Motion (7 features):} Mean and standard deviation of accelerometer magnitude; mean and standard deviation of gyroscope magnitude; and per-axis accelerometer means ($x$, $y$, $z$).

\subsection{Computing the Deviation Vector}

Given enrollment features $\mathbf{e}$ and test-session features $\mathbf{s}$ (both 42-dimensional after pruning unavailable features), for each shared dimension $i$ we compute:

\begin{equation}
\delta_i^{\text{abs}} = |s_i - e_i|
\end{equation}

\begin{equation}
\delta_i^{\text{rel}} = \begin{cases}
\frac{|s_i - e_i|}{|e_i|} & \text{if } |e_i| > 10^{-6} \\
|s_i| & \text{otherwise}
\end{cases}
\end{equation}

The raw session value $s_i$ is also retained. In addition to these per-dimension triples, four aggregate statistics are appended: the mean and maximum of the absolute deviations and the mean and maximum of the relative deviations. The resulting vector has dimensionality:

\begin{equation}
d = 3 \times 40 + 4 = 124 \text{ dimensions}
\end{equation}

The intuition behind this representation is direct. A genuine user's deviation values cluster near zero because motor behavior is habitual and self-consistent. An impostor carrying different motor habits produces elevated deviations scattered across multiple dimensions. The classification task therefore reduces to separating low-deviation vectors from high-deviation ones.

\begin{figure}[htbp]
\centering
\resizebox{\columnwidth}{!}{%
\begin{tikzpicture}[
    box/.style={draw, rounded corners, minimum height=0.65cm, align=center, font=\scriptsize},
    arrow/.style={-{Stealth[length=2mm]}, thick},
    node distance=0.35cm and 0.25cm
]
\node[box, fill=blue!15, minimum width=1.9cm] (enroll) {Enrollment\\Session};
\node[box, fill=blue!8, right=0.5cm of enroll, minimum width=1.7cm] (eraw) {Raw Features\\$\mathbf{e}$ (42-dim)};
\draw[arrow] (enroll) -- (eraw);

\node[box, fill=red!15, minimum width=1.9cm, below=0.6cm of enroll] (test) {Test\\Session};
\node[box, fill=red!8, right=0.5cm of test, minimum width=1.7cm] (traw) {Raw Features\\$\mathbf{s}$ (42-dim)};
\draw[arrow] (test) -- (traw);

\node[box, fill=orange!20, minimum width=2.1cm, right=0.5cm of $(eraw.east)!0.5!(traw.east)$] (dev) {Deviation\\Computation\\$\delta^{\text{abs}}, \delta^{\text{rel}}, s_i$};
\draw[arrow] (eraw.east) -- ++(0.2,0) |- (dev.west);
\draw[arrow] (traw.east) -- ++(0.2,0) |- (dev.west);

\node[box, fill=green!18, right=0.5cm of dev, minimum width=1.6cm] (out) {\textbf{124-dim}\\Feature Vector};
\draw[arrow] (dev) -- (out);

\end{tikzpicture}%
}
\caption{Feature pipeline. Each session's raw features are compared element-wise against the enrollment baseline to produce a 124-dimensional deviation vector for classification.}
\label{fig:feature_pipeline}
\end{figure}


% ====================================================================
\section{Machine Learning Methodology}
\label{sec:ml}
% ====================================================================

\subsection{Dataset Construction}

Collecting behavioral biometric data from a sufficiently large participant pool posed the single greatest practical challenge of this project. Ethics clearance, participant recruitment, and the need for multiple sessions per individual --- one enrollment session, three genuine sessions, and three impostor sessions where a different person operates the enrolled device --- consumed a disproportionate share of the available timeline. The final real-data pool comprised 8 participants (P01 through P08).

A dataset of this size is insufficient for robust classifier training. To address this, we constructed a synthetic data augmentation pipeline in Python. The generation procedure operates as follows:

\begin{enumerate}
\item Detailed behavioral profiles are extracted from each of the 8 real users, encompassing per-digit dwell time distributions, flight time statistics, touch velocity and pressure characteristics, and accelerometer/gyroscope magnitude patterns.
\item Fifty synthetic participants (P09 through P58) are generated. Each synthetic profile is constructed by blending 2 to 3 randomly selected real profiles using Dirichlet-distributed interpolation weights, followed by perturbation with multiplicative Gaussian noise ($\mu = 1.0$, $\sigma = 0.15$).
\item Age-group speed modifiers are applied based on motor-control literature~\cite{ketcham2002aging}. The younger bracket (ages 18--25) exhibits approximately 15\% faster typing speeds, while the older bracket (ages 46--60) is 35--45\% slower. These modifiers derive from published ergonomics research rather than from our own measured data.
\item Each synthetic participant receives unique per-digit rhythm offsets. Digit-position timing emerged as one of the most individually discriminative signals in the real data, and preserving this characteristic in the synthetic pool was deemed essential.
\item Motion-sensor data is generated using an Ornstein--Uhlenbeck random walk rather than i.i.d.\ Gaussian sampling. Accelerometer time series exhibit strong temporal autocorrelation; independent Gaussian noise would produce unrealistically discontinuous traces.
\item Impostor sessions are generated by substituting the profile of a \emph{different} synthetic participant, rather than adding noise to the target profile. Noising the target would produce an impostor distribution that is merely a smoothed version of the genuine distribution, artificially simplifying the classification boundary.
\end{enumerate}

The resulting dataset contains 379 sessions: 174 labelled genuine and 205 labelled impostor.

\subsection{Classifier Selection}

Three classifiers were evaluated, each selected for a distinct reason:

\textbf{Random Forest:} Configured with 300 estimators, maximum depth of 12, minimum samples for split set to 3, minimum samples per leaf set to 2, and balanced class weights. Random Forest was chosen both for its established effectiveness on tabular data and because Gini importance scores are computed as a byproduct of training, which we required for the feature importance analysis in Section~\ref{sec:results}.

\textbf{Multi-Layer Perceptron:} Three hidden layers of 128, 64, and 32 units with ReLU activations, trained using Adam with a 15\% held-out validation split for early stopping, L2 regularization ($\alpha = 0.0005$), and a maximum of 1000 epochs. The MLP was selected specifically for its deployability: weight matrices and bias vectors can be serialized to a JSON file and the forward pass reimplemented as Kotlin matrix-vector multiplications. This eliminates any dependency on TensorFlow Lite, ONNX Runtime, or native libraries, keeping the APK lightweight.

\textbf{One-Class SVM:} RBF kernel with $\gamma$ set to scale and $\nu = 0.1$, trained exclusively on genuine session data. This formulation is conceptually well suited to authentication because it models normalcy without requiring impostor examples. In practice, however, it produced the weakest results among the three classifiers.

\subsection{Evaluation Protocol}

Random Forest and MLP were evaluated using five-fold stratified cross-validation with class balance preserved within each fold. Reported metrics include accuracy, precision, recall, F1 score, AUC-ROC, and equal error rate (EER). For the One-Class SVM, whose output is a decision function score rather than a probability, we applied min-max normalization to the range $[0, 1]$ prior to computing AUC and EER.

\subsection{Hybrid Detection Engine}
\label{sec:hybrid}

The on-device detection system does not rely on the MLP alone. A parallel Z-score track operates alongside it, motivated by a practical timing constraint: during the first 10 to 15 seconds of a session, insufficient data has accumulated to construct a full 124-feature deviation vector, but the Z-score comparator can identify gross deviations using whatever partial data is available.

\textbf{Z-score track.} At 15-second intervals, the \texttt{BehaviorAnalyzer} class retrieves current-session keystroke, touch, and motion averages from the Room database and compares them against the enrollment baseline. Keystroke deviation is a weighted combination of dwell-time and flight-time Z-scores --- 25\% and 75\% respectively. Flight time receives the higher weight because the dwell-time measurement from the stock keyboard is a fixed estimate (80\,ms), rendering its Z-score essentially uninformative. Touch and motion deviations use percentage change. The combined Z-score risk is:

\begin{equation}
R_Z = 0.35 \cdot d_k + 0.30 \cdot d_t + 0.35 \cdot d_m
\end{equation}

\textbf{ML track.} This track activates once at least 6 keystroke events and 50 motion samples have been collected. The feature extractor computes the full deviation vector, the inference engine applies the StandardScaler parameters saved from training, and the forward pass executes:

\begin{equation}
\begin{split}
p(\text{genuine} \mid \mathbf{x}) &= \sigma\!\big(\mathbf{W}_4 \cdot \text{ReLU}(\mathbf{W}_3 \cdot \text{ReLU}( \\
&\quad \mathbf{W}_2 \cdot \text{ReLU}(\mathbf{W}_1 \mathbf{z} + \mathbf{b}_1) + \mathbf{b}_2) + \mathbf{b}_3) + \mathbf{b}_4\big)
\end{split}
\end{equation}

\textbf{Score fusion.} The two risk scores are combined with 60\% weight on the ML track and 40\% on the Z-score track:

\begin{equation}
R = 0.4 \cdot R_Z + 0.6 \cdot R_{\text{ML}}
\end{equation}

This weighting was determined empirically. We experimented with 50/50 and 70/30 splits during live device testing; 60/40 produced the best balance between false alarm suppression and impostor detection sensitivity across our test sessions. The fused score passes through an exponential moving average filter ($\alpha = 0.3$) to attenuate transient noise, then maps to one of four risk levels.

\begin{figure}[htbp]
\centering
\resizebox{\columnwidth}{!}{%
\begin{tikzpicture}[
    box/.style={draw, rounded corners, minimum height=0.6cm, align=center, font=\scriptsize},
    decision/.style={draw, diamond, aspect=2, inner sep=1pt, font=\scriptsize, align=center},
    arrow/.style={-{Stealth[length=2mm]}, thick},
    node distance=0.4cm and 0.3cm
]
\node[box, fill=gray!15, minimum width=2.2cm] (input) {Live Session Data\\(keystrokes, touch, motion)};

\node[box, fill=blue!15, below left=0.7cm and 0.3cm of input, minimum width=1.8cm] (zscore) {\textbf{Z-Score}\\Pathway\\$R_Z$};
\node[box, fill=orange!15, below right=0.7cm and 0.3cm of input, minimum width=1.8cm] (mlpath) {\textbf{MLP Neural}\\Network\\$R_{\text{ML}}$};

\draw[arrow] (input.south) -- ++(0,-0.2) -| (zscore.north);
\draw[arrow] (input.south) -- ++(0,-0.2) -| (mlpath.north);

\node[box, fill=green!18, below=1.0cm of input, minimum width=2.2cm] (fusion) {\textbf{Score Fusion}\\$R = 0.4\,R_Z + 0.6\,R_{\text{ML}}$};
\draw[arrow] (zscore.south) -- ++(0,-0.15) -| (fusion.west);
\draw[arrow] (mlpath.south) -- ++(0,-0.15) -| (fusion.east);

\node[box, fill=yellow!15, below=0.35cm of fusion, minimum width=2.2cm] (ema) {Exponential Moving\\Average ($\alpha=0.3$)};
\draw[arrow] (fusion) -- (ema);

\node[box, fill=green!30, below left=0.6cm and 1.0cm of ema, minimum width=1.2cm] (low) {LOW\\Continue};
\node[box, fill=yellow!40, below left=0.6cm and -0.15cm of ema, minimum width=1.2cm] (med) {MED\\Warning};
\node[box, fill=orange!40, below right=0.6cm and -0.15cm of ema, minimum width=1.2cm] (high) {HIGH\\Re-auth};
\node[box, fill=red!35, below right=0.6cm and 1.0cm of ema, minimum width=1.2cm] (crit) {CRIT\\Logout};

\draw[arrow] (ema.south) -- ++(0,-0.2) -| (low.north);
\draw[arrow] (ema.south) -- ++(0,-0.2) -| (med.north);
\draw[arrow] (ema.south) -- ++(0,-0.2) -| (high.north);
\draw[arrow] (ema.south) -- ++(0,-0.2) -| (crit.north);

\end{tikzpicture}%
}
\caption{The hybrid detection pipeline. Two parallel tracks (statistical Z-score and neural network) are fused, smoothed, and mapped to a graduated security response.}
\label{fig:hybrid}
\end{figure}

\begin{table}[htbp]
\caption{Risk Levels and Corresponding Security Responses}
\label{tab:risk_levels}
\centering
\begin{tabular}{lcc}
\toprule
\textbf{Risk Level} & \textbf{Score Range} & \textbf{Action Taken} \\
\midrule
Low & $[0.0, 0.2)$ & Continue normally \\
Medium & $[0.2, 0.4)$ & Show warning banner \\
High & $[0.4, 0.6)$ & Demand re-authentication \\
Critical & $[0.6, 1.0]$ & Force logout immediately \\
\bottomrule
\end{tabular}
\end{table}

The thresholds in Table~\ref{tab:risk_levels} are uniform across all users and were calibrated manually during on-device testing. Per-user threshold adaptation would likely improve both precision and recall but was not implemented in this prototype.


% ====================================================================
\section{Experimental Results}
\label{sec:results}
% ====================================================================

\subsection{Classifier Comparison}

Table~\ref{tab:model_comparison} summarizes the performance of each classifier on the 379-session dataset.

\begin{table}[htbp]
\caption{Classifier Performance Under 5-Fold Cross-Validation}
\label{tab:model_comparison}
\centering
\begin{tabular}{l c c c c c c}
\toprule
\textbf{Model} & \textbf{Acc.} & \textbf{Prec.} & \textbf{Rec.} & \textbf{F1} & \textbf{AUC} & \textbf{EER} \\
\midrule
Random Forest & 0.897 & 0.952 & 0.836 & 0.890 & 0.979 & 0.087 \\
MLP (deployed) & 0.876 & 0.894 & 0.852 & 0.873 & 0.938 & 0.145 \\
One-Class SVM & 0.821 & 0.807 & 0.841 & 0.824 & 0.908 & 0.238 \\
\bottomrule
\end{tabular}
\end{table}

Random Forest outperforms both alternatives across every metric. At 89.71\% accuracy, 95.18\% precision, an AUC of 0.979, and an EER of 8.71\%, it provides the strongest overall discrimination. The 95\% precision figure is particularly significant in a financial context: it means that when the model classifies a session as legitimate, that classification is correct approximately 19 times out of 20. False acceptance --- granting access to an unauthorized user --- is the costlier error in banking, and a 5\% false acceptance rate represents a reasonable operating point.

The MLP achieves 87.60\% accuracy with an AUC of 0.938, trailing Random Forest primarily on EER (14.51\% versus 8.71\%). The practical consideration that led us to deploy the MLP rather than the more accurate Random Forest is computational: executing 300 decision trees on a mobile device requires serializing every tree structure, traversing each tree independently, and aggregating 300 vote outcomes. By contrast, the MLP forward pass consists of four matrix-vector multiplications, which is substantially less code and uses less memory.

The One-Class SVM produced the weakest results: 82.06\% accuracy and 23.76\% EER. By training exclusively on genuine sessions, this formulation discards all impostor examples, and with a 124-dimensional feature space of moderate size, the resulting support is evidently too loose to maintain acceptable separation.

\begin{figure}[htbp]
\centering
\begin{tikzpicture}
\begin{axis}[
    width=0.95\columnwidth,
    height=6.5cm,
    xlabel={False Positive Rate},
    ylabel={True Positive Rate},
    xmin=0, xmax=1,
    ymin=0, ymax=1,
    grid=major,
    grid style={gray!30},
    legend style={at={(0.98,0.02)}, anchor=south east, font=\scriptsize, draw=gray!50},
    tick label style={font=\scriptsize},
    label style={font=\small},
]

\addplot[blue, thick, mark=none, smooth] coordinates {
    (0.0,0.0) (0.0,0.35) (0.01,0.55) (0.037,0.65)
    (0.042,0.70) (0.053,0.74) (0.079,0.78) (0.095,0.80)
    (0.137,0.84) (0.168,0.87) (0.189,0.90) (0.221,0.92)
    (0.274,0.94) (0.337,0.955) (0.400,0.965) (0.484,0.975)
    (0.579,0.985) (0.700,0.99) (0.842,0.995) (1.0,1.0)
};
\addlegendentry{RF (AUC=0.979)}

\addplot[red, thick, dashed, mark=none, smooth] coordinates {
    (0.0,0.0) (0.0,0.20) (0.02,0.40) (0.05,0.55)
    (0.08,0.63) (0.11,0.70) (0.15,0.76) (0.20,0.81)
    (0.26,0.855) (0.32,0.89) (0.40,0.92) (0.48,0.94)
    (0.55,0.955) (0.63,0.97) (0.74,0.98) (0.85,0.99)
    (1.0,1.0)
};
\addlegendentry{MLP (AUC=0.938)}

\addplot[green!60!black, thick, dotted, mark=none, smooth] coordinates {
    (0.0,0.0) (0.02,0.12) (0.05,0.30) (0.10,0.45)
    (0.15,0.56) (0.20,0.64) (0.27,0.72) (0.34,0.78)
    (0.42,0.83) (0.50,0.87) (0.58,0.90) (0.66,0.93)
    (0.75,0.955) (0.85,0.975) (0.93,0.99) (1.0,1.0)
};
\addlegendentry{OCSVM (AUC=0.908)}

\addplot[gray, thin, dashed] coordinates {(0,0) (1,1)};

\end{axis}
\end{tikzpicture}
\caption{ROC curves for the three classifiers. Random Forest achieves the tightest approach to the upper-left corner.}
\label{fig:roc}
\end{figure}

\subsection{Feature Importance Analysis}

Table~\ref{tab:feature_importance} lists the ten highest-ranked features by Random Forest Gini importance. The ranking produced a result counter to our initial expectations.

\begin{table}[htbp]
\caption{Ten Most Important Features (Random Forest)}
\label{tab:feature_importance}
\centering
\small
\begin{tabular}{r l c}
\toprule
\textbf{\#} & \textbf{Feature Name} & \textbf{Importance} \\
\midrule
1 & dev\_motion\_accel\_y\_mean\_abs & 0.0907 \\
2 & dev\_motion\_accel\_z\_mean\_rel & 0.0775 \\
3 & dev\_motion\_accel\_y\_mean\_rel & 0.0749 \\
4 & dev\_motion\_accel\_z\_mean\_abs & 0.0731 \\
5 & dev\_touch\_tap\_ratio\_rel & 0.0603 \\
6 & dev\_motion\_accel\_mag\_mean\_abs & 0.0585 \\
7 & dev\_touch\_tap\_ratio\_abs & 0.0447 \\
8 & dev\_motion\_accel\_mag\_mean\_rel & 0.0381 \\
9 & dev\_motion\_accel\_x\_mean\_abs & 0.0257 \\
10 & overall\_rel\_deviation & 0.0212 \\
\bottomrule
\end{tabular}
\end{table}

Seven of the top ten features derive from accelerometer data. The single strongest discriminator is the absolute deviation of mean Y-axis acceleration, which corresponds to forward-and-backward tilt when the handset is in portrait orientation. The second-ranked feature is the relative deviation of Z-axis acceleration, encoding shifts in gravitational alignment. We had anticipated that keystroke timing would dominate the rankings. It did not.

The explanation, in hindsight, is not difficult to see. Phone-holding posture is an automatic motor habit formed over months and years of device use. No one consciously decides to tilt the screen to 37 degrees; the angle is a product of accumulated ergonomic preference. Critically, these posture differences are large in magnitude between individuals, highly stable within an individual across sessions, and invisible to an external observer. An attacker looking over a user's shoulder can observe the keys being typed but cannot determine the angular orientation of the display.

Tap ratio --- the proportion of touch events classified as taps versus swipes --- appears at ranks 5 and 7. This feature captures navigation style: some users interact with the interface primarily through discrete taps, while others rely heavily on swiping and scrolling gestures. During our data collection, this behavioral split proved remarkably consistent within individuals across sessions.

Keystroke-derived features, including PIN dwell time deviation and per-digit rhythm values, first appear around rank 12 and are distributed across ranks 20 through 40. The per-digit rhythm features suffer from an importance fragmentation effect: because the ``typing rhythm'' concept is distributed across six digit-position-specific features, each individual feature captures only a fraction of the total contribution. Aggregated, their combined weight would be substantially higher, but the Random Forest importance calculation treats each feature independently.

\begin{figure}[htbp]
\centering
\begin{tikzpicture}
\begin{axis}[
    xbar,
    width=0.95\columnwidth,
    height=7.5cm,
    bar width=7pt,
    xmin=0, xmax=0.10,
    xlabel={Gini Importance},
    xlabel style={font=\small},
    tick label style={font=\tiny},
    ytick=data,
    yticklabels={
        {overall\_rel\_dev},
        {accel\_x\_abs},
        {accel\_mag\_rel},
        {tap\_ratio\_abs},
        {accel\_mag\_abs},
        {tap\_ratio\_rel},
        {accel\_z\_abs},
        {accel\_y\_rel},
        {accel\_z\_rel},
        {accel\_y\_abs}
    },
    y dir=reverse,
    nodes near coords,
    nodes near coords style={font=\tiny, /pgf/number format/fixed, /pgf/number format/precision=3},
    every node near coord/.append style={anchor=west},
    enlarge y limits={abs=0.5},
    grid=major,
    grid style={gray!20},
    xmajorgrids=true,
    ymajorgrids=false,
]
\addplot[fill=blue!50, draw=blue!70] coordinates {
    (0.0907,0) (0.0775,1) (0.0749,2) (0.0731,3)
    (0.0603,4) (0.0585,5) (0.0447,6) (0.0381,7)
    (0.0257,8) (0.0212,9)
};
\end{axis}
\end{tikzpicture}
\caption{Top-10 feature importances. Motion (accelerometer) features dominate, followed by touch interaction style.}
\label{fig:feature_importance}
\end{figure}

\subsection{On-Device Performance}

The deployed MLP comprises 26,273 parameters across four layers ($124 \to 128 \to 64 \to 32 \to 1$). The serialized weight file occupies approximately 450\,KB in JSON format. A single forward pass completes in under 1\,ms on the Snapdragon 680. The complete risk assessment cycle --- encompassing the Room database query, feature extraction, MLP inference, Z-score computation, score fusion, and EMA update --- runs at a median latency of 200\,ms. Given the 15-second interval between analysis cycles, this latency is negligible. No participant in our testing reported perceptible lag or battery impact.


% ====================================================================
\section{Discussion}
\label{sec:discussion}
% ====================================================================

\subsection{The Soft Keyboard Problem}

The most significant limitation in our data collection pipeline concerns keystroke timing on the standard Android keyboard. The 80\,ms dwell time assigned to general text input is not a measurement --- it is a constant derived from average tap durations observed during the pilot phase. Android's input method architecture delivers text to the application but withholds the underlying touch events. Flight time, computed from \texttt{TextFieldValue} timestamps, is a genuine measurement in principle, but in practice it absorbs variable latency introduced by the keyboard's autocorrect and prediction logic between the physical tap and the character reaching the text field.

The custom PIN pad circumvents this limitation entirely, providing real touch-down and touch-up timestamps, but its scope is narrow: six digits entered at login. Implementing a full custom input method editor would extend accurate keystroke capture to all text entry throughout the session. However, doing so would require users to switch away from their preferred keyboard, which runs counter to the transparency principle guiding our design. For a banking application whose security mechanism is supposed to operate invisibly, introducing keyboard-switching friction was judged unacceptable.

The downstream effect is visible in the feature importance analysis: keystroke features contribute to classification but do not dominate the rankings. Whether this outcome reflects a genuine weakness of keystroke dynamics on mobile or is primarily an artifact of measurement noise remains an open question that a custom-IME implementation could resolve.

\subsection{Synthetic Data Validity}

Fifty of the 58 participants in our evaluation are synthetic, and this ratio warrants scrutiny. The generation pipeline can only recombine and perturb behavioral characteristics already present in the 8 real users from whom the profiles originate. If those 8 individuals share a demographic or postural trait --- for instance, all being right-handed college-age students who hold their phones at similar angles --- the synthetic pool would inherit that bias without any mechanism to counteract it.

Several design decisions were made to mitigate this risk. Dirichlet blending produces composite profiles that do not correspond to any single real participant. Age-group speed modifiers, drawn from published motor-control research~\cite{ketcham2002aging}, introduce systematic variation in typing speed and accuracy rather than relying solely on random perturbation. The Ornstein--Uhlenbeck noise model for motion data preserves the temporal autocorrelation structure that independent Gaussian sampling would destroy. Impostor sessions use a genuinely different participant's profile rather than a noisy copy of the target profile.

These measures improve the plausibility of the synthetic data but do not eliminate the underlying dependency on a small real pool. A properly powered validation study with 30 or more real participants remains the most important next step for establishing the generalizability of these results.

\subsection{Privacy}

All behavioral data and all inference computation remain on the device. No behavioral profiles are transmitted to a server; no network calls are required for authentication decisions.

Two gaps in the current prototype should be acknowledged. First, the CSV export functionality built for research purposes writes raw behavioral traces to external storage in unencrypted form. In any deployment beyond the research context, this feature would need to be removed or gated behind encrypted access. Second, the Room database stores behavioral data without encryption; integrating SQLCipher would address this with minimal architectural change but was deprioritized during prototyping.

Behavioral data carries inherent re-identification risk~\cite{de2013unique}. Even ostensibly anonymized timing patterns can be linked to specific individuals given sufficient samples. The on-device architecture eliminates the most common exposure vectors --- there is no server to breach and no data in transit to intercept --- but does not protect against physical access. A rooted device, an ADB backup, or forensic disk imaging could yield the local database contents.

\subsection{Adversarial Resilience}

Two categories of attack merit consideration:

\textbf{Enrollment poisoning.} The entire system assumes that the person performing the enrollment session is the legitimate account holder. If an attacker completes enrollment using their own behavioral profile, all subsequent sessions from the true owner will be flagged as anomalous. Defending against this scenario requires multi-session enrollment distributed across several days, combined with an external identity verification step such as document scanning or in-person confirmation. This defense was not implemented in the current prototype.

\textbf{Behavioral mimicry.} Published research on keystroke dynamics suggests that deliberately imitating another person's typing rhythm is difficult to sustain beyond a small number of characters~\cite{teh2017keystroke}. Our system raises the bar further by incorporating touch interaction patterns and accelerometer-derived holding posture alongside keystroke timing. A successful mimicry attack would require simultaneously reproducing the target's typing rhythm, touch behavior (tap-versus-swipe ratio, velocity, pressure), and phone-holding angle. The dominance of accelerometer features in the importance rankings is relevant here: device-holding posture operates below conscious awareness, is not externally observable, and would be extremely difficult for an attacker to replicate even with knowledge that this signal is being captured.

\subsection{Comparison with Prior Work}

The 8.71\% EER achieved by Random Forest falls within the 5--12\% range reported by Killourhy and Maxion~\cite{killourhy2009comparing} for fixed-text keystroke dynamics on hardware keyboards. Our evaluation setting is arguably more challenging: it uses a mobile soft keyboard, fuses multiple modalities, and evaluates across separate sessions rather than within a single recording. The AUC of 0.979 is consistent with the strongest results surveyed by Zheng et al.~\cite{zheng2020survey} and Patel et al.~\cite{patel2016continuous}.

Direct quantitative comparison across studies in this area is inherently limited because datasets, feature representations, and evaluation protocols differ substantially between research groups. Within these constraints, the results indicate that combining a lightweight statistical anomaly detector with a compact neural network provides a viable architecture for continuous on-device authentication in mobile banking applications.


% ====================================================================
\section{Conclusion and Future Directions}
\label{sec:conclusion}
% ====================================================================

SecureBank demonstrates that continuous behavioral authentication can be implemented within a functioning banking application on commodity Android hardware. The system captures keystroke timing, touch interaction patterns, and motion-sensor readings from login onward, computes enrollment-relative deviation features, and processes them through two parallel detection tracks --- one statistical, one neural --- whose outputs are fused into a single risk score. The response graduates from passive monitoring through warning banners to re-authentication demands and forced logout.

Random Forest achieved 89.71\% accuracy with an 8.71\% EER under cross-validation. The MLP deployed on-device accepts a modest accuracy reduction in exchange for substantially simpler inference execution. The Z-score track provides coverage during the opening seconds of a session before the MLP has accumulated sufficient data. The most noteworthy finding from the feature importance analysis was the dominance of accelerometer tilt over keystroke timing in the rankings, although this outcome is partially attributable to the soft-keyboard measurement constraints discussed above.

Five directions would strengthen the system if pursued in future work:

\begin{enumerate}
\item A user study involving 30 or more real participants would reduce dependence on synthetic data augmentation and provide a more robust test of generalizability.
\item Adaptive enrollment baselines are needed to accommodate behavioral drift over time. Changes in phone case, typing habits, and posture preferences would otherwise cause false rejection rates to increase progressively.
\item Temporal sequence models such as LSTMs or Transformers operating on raw event streams could capture ordering and timing patterns lost by the current pre-aggregation approach.
\item Integration with Android's \texttt{BiometricPrompt} API would allow re-authentication challenges to use the system's native fingerprint or face recognition interface, avoiding custom UI that may feel intrusive.
\item A formal usability evaluation should measure the rate of false rejections experienced by legitimate users and assess whether security prompts are perceived as acceptable or disruptive. An authentication system that users disable is no authentication system at all.
\end{enumerate}

Source code, the data generation pipeline, and trained model weights are made publicly available to facilitate replication and extension of this work.


% ====================================================================
% REFERENCES
% ====================================================================

\begin{thebibliography}{00}

\bibitem{ecb2022}
European Central Bank, ``Fifth report on card fraud,'' \textit{ECB Statistical Paper Series}, 2022.

\bibitem{fbi2023}
Federal Bureau of Investigation, ``Internet Crime Report 2023,'' \textit{IC3 Annual Report}, 2023.

\bibitem{teh2017keystroke}
P.~S. Teh, A.~B.~J. Teoh, and S. Yue, ``A survey of keystroke dynamics biometrics,'' \textit{The Scientific World Journal}, vol. 2013, pp. 1--24, 2013.

\bibitem{bo2013silentsense}
C.~Bo, L.~Zhang, X.-Y.~Li, Q.~Huang, and Y.~Wang, ``SilentSense: Silent user identification via touch and movement behavioral biometrics,'' in \textit{Proc. ACM MobiCom}, 2013, pp. 187--190.

\bibitem{frank2013touchalytics}
M.~Frank, R.~Biedert, E.~Ma, I.~Martinovic, and D.~Song, ``Touchalytics: On the applicability of touchscreen input as a behavioral biometric for continuous authentication,'' \textit{IEEE Trans. Inf. Forensics Security}, vol.~8, no.~1, pp. 136--148, Jan. 2013.

\bibitem{zheng2020survey}
N.~Zheng, K.~Bai, H.~Huang, and H.~Wang, ``You are how you touch: User verification on smartphones via tapping behaviors,'' in \textit{Proc. IEEE 22nd Int. Conf. Network Protocols (ICNP)}, 2014, pp. 348--359.

\bibitem{monrose1997keystroke}
F.~Monrose and A.~D.~Rubin, ``Authentication via keystroke dynamics,'' in \textit{Proc. 4th ACM Conf. Computer and Communications Security}, 1997, pp. 48--56.

\bibitem{killourhy2009comparing}
K.~S.~Killourhy and R.~A.~Maxion, ``Comparing anomaly-detection algorithms for keystroke dynamics,'' in \textit{Proc. IEEE/IFIP Int. Conf. Dependable Systems \& Networks (DSN)}, 2009, pp. 125--134.

\bibitem{giuffrida2014itsme}
C.~Giuffrida, K.~Majdanik, M.~Conti, and H.~Bos, ``I sensed it was you: Authenticating mobile users with sensor-enhanced keystroke dynamics,'' in \textit{Proc. DIMVA}, 2014, pp. 92--111.

\bibitem{buschek2015touchalytics}
D.~Buschek, A.~De~Luca, and F.~Alt, ``Improving accuracy, applicability and usability of keystroke biometrics on mobile touchscreen devices,'' in \textit{Proc. ACM CHI}, 2015, pp. 1393--1402.

\bibitem{conti2011mobileauth}
M.~Conti, I.~Zachia-Zlatea, and B.~Crispo, ``Mind how you answer me! Transparently authenticating the user of a smartphone when answering or placing a call,'' in \textit{Proc. ACM ASIACCS}, 2011, pp. 249--260.

\bibitem{sitova2016hmog}
Z.~Sitov\'{a} et~al., ``HMOG: New behavioral biometric features for continuous authentication of smartphone users,'' \textit{IEEE Trans. Inf. Forensics Security}, vol.~11, no.~5, pp. 877--892, May 2016.

\bibitem{patel2016continuous}
V.~M.~Patel, R.~Chellappa, D.~Chandra, and B.~Barbello, ``Continuous user authentication on mobile devices: Recent progress and remaining challenges,'' \textit{IEEE Signal Processing Magazine}, vol.~33, no.~4, pp. 49--61, Jul. 2016.

\bibitem{khan2014gait}
H.~Khan and U.~Hengartner, ``Towards application-centric implicit authentication on smartphones,'' in \textit{Proc. ACM WiSec}, 2014, pp. 10--21.

\bibitem{li2020continuous}
M.~Abuhamad, T.~Abuhmed, D.~Mohaisen, and D.~Nyang, ``AUToSen: Deep-learning-based implicit continuous authentication using smartphone sensors,'' \textit{IEEE Internet of Things Journal}, vol.~7, no.~6, pp. 5008--5020, Jun. 2020.

\bibitem{ketcham2002aging}
C.~J.~Ketcham and G.~E.~Stelmach, ``Age-related declines in motor control,'' in \textit{Handbook of the Psychology of Aging}, Academic Press, 2002, pp. 313--348.

\bibitem{de2013unique}
Y.-A.~de~Montjoye, C.~A.~Hidalgo, M.~Verleysen, and V.~D.~Blondel, ``Unique in the crowd: The privacy bounds of human mobility,'' \textit{Scientific Reports}, vol.~3, no.~1376, 2013.

\end{thebibliography}

\end{document}
